Federated Imputation

### 2020-06-24 federated_imp_synthesizing_complete_data.Rmd
Added multivariate normal example

>>>>

# Synthpop estimates

Synthetic data estimates $(\hat{\beta_1}, \hat{\beta_2}, \dots, \hat{\beta_m})$ - if the model for the data is correct, the $m$ estimates from the synthetic data will be centered around the estimate $\hat{\beta}$ that would have been obtained from the observed data. If the method of inference used to fit the model provides consistent estimates of the parameters and the same is true for the analyses of the synthetic data, then the mean of $m$ synthetic estimates, $\bar{\hat{\beta}}=\sum_{i=1}^m\hat{\beta_i}/m$ provides a consistent estimate of $\hat{\beta}$. Provided that the observed and synthetic data are generated by the common sampling scheme, then $V_{\bar{\hat{\beta}}}=\sum_{i=1}^m V_{\hat{\beta_i}}/m$ will be a consistent estimate of $V_{\hat{\beta}}$.

The variance-covariance matrix of $\bar{\hat{\beta}}$, conditional on $\hat{\beta}$ and $V_{\hat{\beta}}$, becomes $V_{\hat{\beta}}$ which can be estimated from $V_{\bar{\hat{\beta}}}/m$.  Thus the stochastic error in the mean of the synthetic estimates aboutthe values from the observed data can be reduced to a negligible quantity by increasing $m$. It must be remembered, however that the consistency of $\bar{\hat{\beta}}$ only applies when observed data are a sample from the distribution used for synthesis. In practical applications  differences between the analyses on the observed data and those from the mean of the syntheses will be found because the data do not conform to the model used for synthesis.  Such differences will not be reduced by increasing $m$. The synthesiser, with access to the observed data, can estimate $\bar{\hat{\beta}}-\hat{\beta}$ and compare it to its standard error in order to judge the extent that this model mismatch affects the estimates.

# Multivariate normal simulated data

```{r, include = F}
source("2.c Synthesize data mvnorm.R")
```

## Synthesizing by a linear regression model

```{r, echo = F}
knitr::kable(synth_by_lm, digits = 3, caption = "Simulation results of multivariate normal data, synthesized by a normal linear regression model.")
```

## Synthesizing by a Classification and Regression Tree (CART)

```{r}
knitr::kable(synth_by_cart, digits = 3, caption = "Simulation results of multivariate normal data, synthesized by classification and regression trees.")
```
